Rough Analysis

### 2023-10-06 Lahman Analysis/Rough Analysis/RoughAnalysis.qmd
Fixed Ulam

@@

```{r}
u1 <- ulam(
  alist(
    HR ~ dnorm(mu, sigma),
    mu <- a + b*(AB - mean_AB),
    #Standard deviation of 20 seems fair to me for home runs in a year
    a ~ dnorm(135, 20),
    #Want to make a very non descriptive prior here since I don't know what the value of b could be
    b ~ dnorm(1, 1),
    sigma ~ dexp(1)
  ), data = Modern.Teams, chains=1
)
```

@@

>>>>

We can see from the `precis` that our `sigma` prior is WAY too small. `precis` tells us its about 40 and we ahve it at 1!

@@

```{r}
slim <- list(
  AB = Modern.Teams$AB,
  HR = Modern.Teams$HR
)

str(slim)
```

```{r}
u1 <- ulam(
  alist(
    HR ~ dnorm(mu, sigma),
    mu <- a + b*(AB - 5368),
    #Standard deviation of 20 seems fair to me for home runs in a year
    a ~ dnorm(135, 20),
    #Want to make a very non descriptive prior here since I don't know what the value of b could be
    b ~ dnorm(1, 1),
    sigma ~ dexp(1)
  ), data = slim, chains=4, cores = 4
)
```

@@

```{r}
traceplot(u1)
```

```{r}
trankplot(u1)
```
